### 2018-02-17 Graduate - Introduction to Analysis II/HW3/3HW20180204.tex
add prob 7, 8

\item Problem IV.4. 2

\item Problem IV. 4.3

>>>>

\item Problem IV.4.2

\textbf{Sol.} Checked https://math.stackexchange.com/questions/2422165/finding-a-closed-rectifiable-curve-with-prescribed-winding-numbers/2422214

Let $\gamma$: $[0, 1] \to \mathbb{C}$ be a union of circles:
$$
\gamma([\frac{1}{2}-\frac{1}{2^n}, \frac{1}{2}-\frac{1}{2^{n+1}}]) = \gamma_1 = B(\frac{1}{2^n}, \frac{1}{2^n}), ~n\ge 1,
$$
and
$$
\gamma([1-\frac{1}{2^n}, 1-\frac{1}{2^{n+1}}]) = \gamma_2 = B(-\frac{1}{2^n}, \frac{1}{2^n}), n \ge 1.
$$
And the direction of $\gamma_1 $ is counterclockwise and $\gamma_2 $ is clockwise.

Then $\gamma$ is rectifiable since length of $\gamma$ is $2\sum_{n=1}^{\infty}2\pi\frac{1}{2^n} = 4\pi$.
Now we show that $\gamma$ is continuous. In fact, we only need to show that $\gamma$ is continuous at the point $t = \frac{1}{2}$ and $t = 1$ since circles are continuous. First we know $\lim_{t\to 1}\gamma(t) = 0 $, hence $\gamma $ is closed. For $\forall \epsilon > 0$, pick $n$, s.t. $\frac{1}{2^n} < \frac{\epsilon}{2}$, then $d(\gamma(t), 0) < 2\times\frac{1}{2^n} < \epsilon$ for all $t\in [1-\frac{1}{2^n}, 1]$. Hence $\gamma$ is continuous at $t = 1$, and similarly, $\gamma$ is continuous at $t = \frac{1}{2}$.

For any integer $k$, if $k > 0$, pick a point $a$ inside the $k^{th} $ largest circle and outside the $(k+1)^{th} $ circle of $\gamma_1 $, then by Proposition 4.1, $n(\gamma; a) = k$. If $k = 0$, pick $a$ outside the largest circle of both $\gamma_1 $ and $\gamma_2 $, then $n(\gamma; a) = 0$.
 If $k < 0$, then pick $a$ inside the $k^{th} $ largest circle and outside the $(k+1)^{th} $ circle of $\gamma_2 $, by Prop 4.1 and Prop 4.3 $n(\gamma; a) = k$.

\item Problem IV.4.3

\textbf{Proof.} By Corollary 3.6, since $p$ is a polynomial of degree $n$, we know
$$
p(z) = c(z-z_1)(z-z_2)\cdots(z-z_n),
$$
where $z_i $ are roots of $p$ and $z_i $ could equal to $z_j $. Then
$$
\frac{p'(z)}{p(z)} = \frac{a\sum_{i=1}^{n}\prod_{j\ne i}^{n}(z-z_j)}{a\prod_{i=1}^{n}(z-z_j)} = \sum_{i=1}^{n}\frac{1}{z-z_i},
$$
with $z_i \in B(0, R) $.
Hence,
$$
\int_{\gamma}\frac{p'(z)}{p(z)}dz = \int_{\gamma}\sum_{i=1}^{n}\frac{1}{z-z_i}dz = \sum_{i=1}^{n}
\int_\gamma\frac{1}{z-z_i}dz = \sum_{i=1}^{n}2\pi i = 2\pi in
$$
by Prop 4.3 and Thm 4.4.
